\begin{thebibliography}{9}

\bibitem{aolDataLeak}
\url{https://www.nytimes.com/2006/08/09/technology/09aol.html}

\bibitem{myspacebreach}
\url{https://www.welivesecurity.com/2016/06/01/myspace-data-breach-360-million-accounts-affected/}
\bibitem{cambridge}
\url{https://it.wikipedia.org/wiki/Scandalo_Facebook-Cambridge_Analytica}

\bibitem{formigli}
\href{https://www.la7.it/piazzapulita/video/la-mia-casa-postata-online-alcune-considerazioni-leditoriale-di-corrado-formigli-12-12-2019-298369}{https://www.la7.it/piazzapulita/video/la-mia-casa-postata-online-alcune-considerazioni-leditoriale-di-corrado-formigli-12-12-2019-298369}

\bibitem{MalandrinoScarano}
Delfina Malandrino e Vittorio Scarano\newline
\textit{Privacy leakage on the Web: Diffusion and countermeasures}\newline
Computer Networks 57.14, 2013

\bibitem{quasiID}
Latanya Sweeney\newline
\textit{Simple demographics often identify people uniquely}\newline
(San Francisco) 671, 2000, pp 1-34

\bibitem{kAnonimity}
Pierangela Samarati, Latanya Sweeney\newline
\textit{Generalizing data to provide anonymity when disclosing information}\newline
PODS Vol. 98 10.1145. Citeseer. 1998, pp. 275487–275508.



\bibitem{looseTweets} 
Huina Mao, Xin Shuaiand Apu Kapadia.\newline
\textit{Loose Tweets: An Analysis of Privacy Leaks on Twitter}. \newline
WPES 2011.


\bibitem{privacyDetective}
Aylin Caliskan, Jonathan Walsh, Rachel Greenstadt.\newline
\textit{Privacy Detective: Detecting Private Information and Collective Privacy Behavior in a Large Social Network}.\newline
WPES 2014

\bibitem{dontTweetThis}
Qiaozhi Wang, Hao Xue, Fengjun Li, Dongwon Lee, and Bo Luo.\newline
\textit{\#DontTweetThis: Scoring Private Information in Social Networks}. \newline
POPETS 2019

\bibitem{dataSpectrum}
John M.M. Rumbold, Barbara K. Pierscionek\newline
\textit{What Are Data? A Categorization of the Data Sensitivity Spectrum}.\newline
2018

\bibitem{Random Forest}
L. Breiman, "Random forests",\newline
Mach. Learn., vol. 45, no. 1, pp. 5-32, 2001.

\bibitem{USE}
Cer, Daniel  and Yang, Yinfei  and Kong, Sheng-yi  and
Hua, Nan  and Limtiaco, Nicole  and St. John, Rhomni  and
Constant, Noah  and Guajardo-Cespedes, Mario  and Yuan, Steve  and
Tar, Chris  and Strope, Brian  and Kurzweil, Ray\newline
\textit{Universal Sentence Encoder}, 2018

\bibitem{yang2019multilingue}
Yinfei Yang, Daniel Cer, Amin Ahmad, Mandy Guo, Jax Law, Noah Constant, Gustavo Hernandez Abrego, Steve Yuan, Chris Tar, Yun-Hsuan Sung, Brian Strope, Ray Kurzweil
\textit{Multilingual Universal Sentence Encoder for Semantic Retrieval}, 2019

\bibitem{inbox}
Douglas Aberdeen, Ondrej Pacovsky  and Andrew Slater\newline
\textit{The Learning Behind Gmail Priority Inbox}, 2010

\bibitem{ds_pol}
Ed King.
\textit{Election Day Tweets}
\url{https://www.kaggle.com/kinguistics/election-day-tweets?select=election_day_tweets.csv}
2020

\bibitem{ds_health1}
Tara Boyle.
\textit{Medical Transcripts}
\url{https://www.kaggle.com/tboyle10/medicaltranscriptions}
2018

\bibitem{ds_health2}
Paul Mooney.
\textit{Medical Speech, Transcription, and Intent}
\url{https://www.kaggle.com/paultimothymooney/medical-speech-transcription-and-intent}
2019

\bibitem{ds_job}
Amir
\textit{Amazon Job skills}
\url{https://www.kaggle.com/atahmasb/amazon-job-skills}
2018

\bibitem{ds_travel}
Figure Eight
\textit{Twitter US Airline Sentiment}
\url{https://www.kaggle.com/crowdflower/twitter-airline-sentiment}
2019

\bibitem{ds_general}
Rounak Banik
\textit{The Movies Dataset}
\url{https://www.kaggle.com/rounakbanik/the-movies-dataset}
2017

\bibitem{PAalgo}
Koby Crammer, Ofer Dekel, Joseph Keshet, Shai Shalev-Shwartz, Yoram Singer\newline
\textit{Online Passive-Aggressive Algorithms}\newline
Journal of Machine Learning Research 7 (2006) 

\bibitem{RocAUC}
Hossin, Mohammad and Sulaiman, MN\newline
\textit{A review on evaluation metrics for data classification evaluations}\newline
International Journal of Data Mining \& Knowledge Management Process, 2015

\bibitem{wu2017visual}
Wu, Qi and Teney, Damien and Wang, Peng and Shen, Chunhua and Dick, Anthony and van den Hengel, Anton\newline
\textit{Computer Vision and Image Understanding}
Computer Vision and Image Understanding, 2017

\bibitem{kaur2017survey}
Kaur, Harpreet and Mangat, Veenu and others\newline
\textit{A survey of sentiment analysis techniques}\newline
2017 International Conference on I-SMAC (IoT in Social, Mobile, Analytics and Cloud)(I-SMAC)

\bibitem{bengio2003neural}
Bengio, Yoshua and Ducharme, R{\'e}jean and Vincent, Pascal and Jauvin, Christian\newline
\textit{A neural probabilistic language model}\newline
Journal of machine learning research, 2003

\bibitem{collobert2008unified}
Collobert, Ronan and Weston, Jason\newline
\textit{A unified architecture for natural language processing: Deep neural networks with multitask learning}\newline
Proceedings of the 25th international conference on Machine learning, 2008

\bibitem{turian2010word}
Turian, Joseph and Ratinov, Lev and Bengio, Yoshua\newline
\textit{Word representations: a simple and general method for semi-supervised learning}\newline
Proceedings of the 48th annual meeting of the association for computational linguistic, 2010

\bibitem{mikolov2013efficient},
Mikolov, Tomas and Chen, Kai and Corrado, Greg and Dean, Jeffrey\newline
\textit{Efficient estimation of word representations in vector space}\newline
arXiv preprint arXiv:1301.3781, 2013

\bibitem{mikolov2013distributed}
Mikolov, Tomas and Sutskever, Ilya and Chen, Kai and Corrado, Greg S and Dean, Jeff\newline
\textit{Distributed representations of words and phrases and their compositionality}\newline
Advances in neural information processing systems, 2013

\bibitem{mnih2007three}
Mnih, Andriy and Hinton, Geoffrey\newline
\textit{Three new graphical models for statistical language modelling}\newline
Proceedings of the 24th international conference on Machine learning, 2007

\bibitem{wang2019user}
Wang, Chenyu and Miao, Zhongchen and Lin, Yuefeng and Gao, Jian\newline
\textit{User and Topic Hybrid Context Embedding for Finance-Related Text Data Mining}\newline
2019 International Conference on Data Mining Workshops (ICDMW), 2019

\bibitem{yang2019online}
Yang, Zhibo and Li, Luyun\newline
\textit{An Online Retrieval Question Answering System for Featured Snippets Triggering}\newline
2019 International Conference on Data Mining Workshops (ICDMW), 2019

\bibitem{arora2016simple}
Arora, Sanjeev and Liang, Yingyu and Ma, Tengyu\newline
\textit{A simple but tough-to-beat baseline for sentence embeddings}
2016

\bibitem{iyyer2015deep}
Iyyer, Mohit and Manjunatha, Varun and Boyd-Graber, Jordan and Daum{\'e} III, Hal\newline
\textit{Deep unordered composition rivals syntactic methods for text classification}\newline
Proceedings of the 53rd Annual Meeting of the Association for Computational Linguistics and the 7th International Joint Conference on Natural Language Processing (Volume 1: Long Papers), 2015

\bibitem{joulin2016fasttext}
Joulin, Armand and Grave, Edouard and Bojanowski, Piotr and Douze, Matthijs and J{\'e}gou, H{\'e}rve and Mikolov, Tomas\newline
\textit{Fasttext. zip: Compressing text classification models}\newline
arXiv preprint arXiv:1612.03651, 2016

\bibitem{chidambaram2018learning}
M. Chidambaram, Y. Yang, D. Cer, S. Yuan, Y. Sung, B. Strope, and R. Kurzweil. \newline
\textit{Learning Cross-Lingual Sentence Representations via a Multi-task Dual-Encoder Model.}, 2018

\bibitem{transfer-learning}
Li, Y., Ngom, A.\newline
\textit{A review on machine learning principles for multi-view biological data integration. Briefings in bioinformatics}\newline
2016

\bibitem{q-learning}
Christopher J. C. H. Watkins, Peter Dayan\newline
\textit{Q-learning}\newline
1992
\bibitem{reinforce-learn}
Csaba Szepesvári\newline
\textit{Algorithms for Reinforcement Learning
Synthesis Lectures on Artificial Intelligence and Machine Learning}\newline
2010

\bibitem{lstm}
Martin Wöllmer, Florian Eyben, Alex Graves, Björn Schuller, Gerhard Rigoll \newline
\textit{Bidirectional LSTM Networks for Context-Sensitive Keyword Detection in a Cognitive Virtual Agent Framework}\newline
2010

\bibitem{collective-data}
Zhipeng Cai et al.\newline
\textit{Collective data-sanitization for preventing sensitive information inference attacks in social networks}.\newline
In: IEEE Transactions on Dependable and Secure Computing 15.4 (2016), pp. 577–590.

\bibitem{collective-data}
Zhipeng Cai et al.\newline
\textit{Collective data-sanitization for preventing sensitive information inference attacks in social networks}\newline
. In: IEEE Transactions on Dependable and Secure Computing 15.4 (2016), pp. 577–590.

\bibitem{diff-privacy}
Cynthia Dwork.\newline
\textit{Differential privacy: A survey of results}.\newline
In: Interna- tional conference on theory and applications of models of computation. Springer. 2008, pp. 1–19.

\bibitem{urwho}
Alan Mislove et al. \newline
\textit{You are who you know: inferring user profiles in online social networks}.\newline
In: Proceedings of the third ACM international conference on Web search and data mining. 2010, pp. 251–260.

\bibitem{inferr-privacy}
Jianming He, Wesley W Chu e Zhenyu Victor Liu. \newline
\textit{Inferring privacy information from social networks}.\newline
In: International Conference on Intelligence and Security Informatics. Springer. 2006, pp. 154–165.

\bibitem{protection-private}
Bo Luo e Dongwon Lee.\newline
\textit{On protecting private information in social networks: a proposal}.\newline
In: 2009 IEEE 25th International Conference on Data Engineering. IEEE. 2009, pp. 1603–1606.

\bibitem{stalking}
Yuhao Yang et al.\newline
\textit{Stalking online: on user privacy in social networks}.\newline
In: Proceedings of the second ACM conference on Data and Application Security and Privacy. 2012, pp. 37–48.

\bibitem{sentiment140}
https://www.kaggle.com/kazanova/sentiment140

\bibitem{studyFb}
Wang, Yang and Norcie, Gregory and Komanduri, Saranga and Acquisti, Alessandro and Leon, Pedro Giovanni and Cranor, Lorrie Faith\newline
\textit{"I regretted the minute I pressed share" a qualitative study of regrets on Facebook}\newline
Proceedings of the seventh symposium on usable privacy and security, pages 1--16, 2011 

\bibitem{readMyTwitter}
Sleeper, Manya and Cranshaw, Justin and Kelley, Patrick Gage and Ur, Blase and Acquisti, Alessandro and Cranor, Lorrie Faith and Sadeh, Norman\newline
\textit{" I read my Twitter the next morning and was astonished" a conversational perspective on Twitter regrets}\newline
Proceedings of the SIGCHI conference on human factors in computing systems, pages 3277--3286, 2013

\bibitem{hybrid}
Cozza, Federico and Guarino, Alfonso and Isernia, Francesco and Malandrino, Delfina and Rapuano, Antonio and Schiavone, Raffaele and Zaccagnino, Rocco\newline
\textit{Hybrid and lightweight detection of third party tracking: Design, implementation, and evaluation}\newline
Computer Networks, 106993, 2020

\bibitem{Koehn07}
Koehn, Philipp and Schroeder, Josh\newline
\textit{Experiments in domain adaptation for statistical machine translation}\newline
Proceedings of the second workshop on statistical machine translation, pages 224--227, 2007

\end{thebibliography}